%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}

\name{Shivam}

\tagline{3rd Year IT Undergraduate }
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{2.5cm}{neerajpc}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{Kumar04shivamy@gmail.com}
    \phone{+91-9210594831}
  \location{Delhi, India}
  \linkedin{linkedin.com/in/shivam-yeshu/}
  
    % \github{github.com/Shivamyeshu} 
    
   

%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Education}

\edu{B.Tech in Information Technology }{ Maharaja Agrasen Institute of Technology }{2023-- Present}{}


\edu{ Diploma in ECE }{Pusa Institute of Technology}{2020-23}{Percentage -  78.6\%}



\cvsection{PROJECTS}

% \cveventnew{\textbf{PharmaTrack 360}}{}{}{2024} 
% \begin{itemize}
% \item Developed a blockchain-powered drug inventory management system using Ethereum, React, and Node.js. Implemented real-time monitoring and secure transaction handling to ensure timely and quality delivery of pharmaceuticals.
% \end{itemize}


% \cveventnew{\textbf{HealthLedger: Blockchain-Powered Medical Record Storer}}{}{Aug 2024}{} \begin{itemize} \item Developed a secure medical record storage platform using Solidity, Ethereum, and React. Implemented decentralized storage with IPFS and ensured data integrity with SHA-256 encryption. \end{itemize}
 % ------------------------------------------------------------------------


% project 1 
\cveventnew{\textbf{Melo}}{}{Dec 2024}{} 
\begin{itemize} 
    \item Melo is a collaborative tool featuring Mesh language documentation with simple syntax, built on Next.js and Docker, offering a shared canvas and an integrated compiler for seamless development.  
    \item It provides an intuitive user interface, streamlining the coding process and reducing setup time for developers.  
\end{itemize}

 % project 2
 \cveventnew{\textbf{Mesh}}{}{Nov 2024}{} 
 \begin{itemize}
 \item Mesh an innovative programming language designed with a custom syntax.
     Built on top of JavaScript.
 \end{itemize}


% projct 3
\cveventnew{\textbf{Ease Explore: AI-Powered Trip Planning App}}{}{July 2024}{} \begin{itemize} \item Created a personalized trip planning app utilizing Next.js, TypeScript, and AI. 
\item Features include AI-driven itinerary generation, cost estimation, and real-time travel updates. The app is branded as "EaseExplore" with the tagline "Simplify Your Adventure." \end{itemize}


% project 4
\cveventnew{\textbf{AyurX Assist }}{}{Feb 2024}{Delhi, India} \begin{itemize} \item Developed an AI chatbot capable of providing 24/7 support, using Botpress and modern web development technologies. The chatbot allows users to describe their symptoms and provides remedies in both Ayurvedic and modern medicine forms. \end{itemize}



% project 5
\cveventnew{\textbf{ Autonomous Obstacle Avoiding Car}}{ }{Feb 2023}{ Delhi, India }
\begin{itemize}
\item  Designed and implemented an autonomous car using ultrasonic sensors for real-time obstacle detection and dynamic path adjustment.

\end{itemize}
% \divider





 \cvsection{ACHIEVEMENTs}
\begin{itemize}

\item\linespread{1.2}Secured a Top 10 rank among over 250 teams in the Inter-College round of SIH (Oct'24)

\item\linespread{1.2}Secured a Top 250 rank among over 25k teams in Flipkart Grid 6.0 Robotics Challenge(Sept'24)

\item\linespread{1.2} Completed 5 days Drone workshop conducted by CDAC,Noida (Aug’24)

\item\linespread{1.2}  Runner Up in Chess competition ( HOURGLASS 4.0 ) at MAIT (Feb’24)

%\item  Secured a Top 3 position in Debate competition, Conducted by IEEE GGSIPU (Dec'23)

\item  Completed a Course of Introduction of Internet Of Thing by Telecom Sector Skill council ( Dec’23 )
\end{itemize}

\clearpage
\end{document}
